\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2023-08-17 docs/papers/sto/so.tex
FIXUP draft minor

\title{\large Neural, Tree, and Symbolic Optimization of Cosmological
Particle-Mesh Simulation
\vspace{0.3em}}

@@

>>>>

\title{\large Neural and Symbolic Optimization of Cosmological
Particle-Mesh Simulation
\vspace{0.3em}}

@@

The SO MLP parameters are initialized in a way such that the MLP output is very
close to one, i.e. no SO.
We achieve this by setting the kernel of the output layer to be very small
random values and the bias to be one.
